\documentclass{article}
\input{packages.tex}

\begin{document}
\input{title.tex}

\makeatletter
\renewcommand{\tableofcontents}{
  \clearpage
  \thispagestyle{empty}
  \begin{center}
          \bfseries\Large\MakeUppercase{Зміст}
  \end{center}
  
  \addvspace{42pt}
  \@starttoc{toc}
}
\renewcommand{\@pnumwidth}{2em}
\renewcommand{\@tocrmarg}{3em}
\makeatother

\cleardoublepage
\pagenumbering{arabic}
\setcounter{page}{1}
\newpage

% Clear the header and footer
\fancyhead{}
\fancyfoot{}
% Set the right side of the footer to be the page number
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{
  \begin{textblock*}{2cm}(20cm,27.3cm) % bottom right corner of A4
    \small\thepage
  \end{textblock*}
}
\pagestyle{fancy}

\newtheorem*{remark}{Зауваження:}

\input{mainreport.tex}

\begin{thebibliography}{99}

    \bibitem{gmp}
    Granlund, T., and the GMP development team.
    \textit{GNU MP: The GNU Multiple Precision Arithmetic Library}.
    Edition 6.3.0, 2023.
    \url{https://gmplib.org/}

    \bibitem{knuth}
    Knuth, D. E.
    \textit{The Art of Computer Programming, Volume 2: Seminumerical Algorithms}.
    3rd edition, Addison-Wesley, 1997.

    \bibitem{karatsuba}
    Karatsuba, A., and Ofman, Y.
    ``Multiplication of Multidigit Numbers on Automata.''
    \textit{Soviet Physics Doklady}, Vol. 7, 1963, pp. 595-596.

    \bibitem{toom}
    Toom, A. L.
    ``The Complexity of a Scheme of Functional Elements Realizing the Multiplication of Integers.''
    \textit{Soviet Mathematics Doklady}, Vol. 3, 1963, pp. 714-716.

    \bibitem{schonhage}
    Schönhage, A., and Strassen, V.
    ``Schnelle Multiplikation großer Zahlen.''
    \textit{Computing}, Vol. 7, 1971, pp. 281-292.

    \bibitem{millerrabin}
    Miller, G. L.
    ``Riemann's Hypothesis and Tests for Primality.''
    \textit{Journal of Computer and System Sciences}, Vol. 13, 1976, pp. 300-317.

    \bibitem{rabin}
    Rabin, M. O.
    ``Probabilistic Algorithm for Testing Primality.''
    \textit{Journal of Number Theory}, Vol. 12, 1980, pp. 128-138.

    \bibitem{montgomery}
    Montgomery, P. L.
    ``Modular Multiplication Without Trial Division.''
    \textit{Mathematics of Computation}, Vol. 44, 1985, pp. 519-521.

    \bibitem{euclid}
    Knuth, D. E.
    ``Analysis of Euclid's Algorithm.''
    \textit{The Art of Computer Programming, Volume 2}, Section 4.5.3, 1997.

    \bibitem{parallel}
    Brent, R. P., and Zimmermann, P.
    \textit{Modern Computer Arithmetic}.
    Cambridge University Press, 2010.

    \bibitem{cryptography}
    Menezes, A. J., van Oorschot, P. C., and Vanstone, S. A.
    \textit{Handbook of Applied Cryptography}.
    CRC Press, 1996.

    \bibitem{numa}
    Lameter, C.
    ``NUMA (Non-Uniform Memory Access): An Overview.''
    \textit{ACM Queue}, Vol. 11, 2013.

\end{thebibliography}

\end{document}
